A young cluster in the Galactic halo: \\ Recent star formation associated with the Magellanic stream

### 2018-05-18 ms.tex
Intro outline

The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies (cite deason, etc.).
The 
(Built up from destroyed satellites that lost their gas on infall)

However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy that can be traced $>360^\circ$ in angle, and the presence of the Magellanic cloud system.
While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC/SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky.
(Gas is great, can run models to try to reproduce. But lacks distance information)
(Many people search for stars associated with the stream, but must be diffuse)

@@

We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream
coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the
mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations
of \citet{Besla2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the
effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric
distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the
position of the position of the cluster with a velocity of \vlsr=70 \kmse.

>>>>

The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
(Gas stripped now too hot/diffuse to form stars)

However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
By modeling the LMC--SMC interaction and infall, ... sims to reproduce gas velocity vs. longitude \citep{Besla:2010}
(But lacks distance constraints)
(Many people search for stars associated with the stream, but must be diffuse)

(Gas near the LMC/SMC is forming stars \citep{Casetti-Dinescu2014,MoniBidin2017}, and cite Deason/Belokurov bridge paper)

@@

We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream
coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the
mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations
of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the
effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric
distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the
position of the position of the cluster with a velocity of \vlsr=70 \kmse.
